Stability concerns in random matrices

### 2018-03-19 random_matrix_stability.Rmd
Add the 20 species plots

```{r, echo = TRUE, eval = TRUE}
gen_var     <- read.table(file = "full_data.csv", header = TRUE, sep = ",");
unstable    <- gen_var[,2] / 1000000;
stable      <- gen_var[,3] / 1000000;
destablised <- gen_var[,4] / 1000000;
stabilised  <- gen_var[,5] / 1000000;
par(mar = c(5, 5, 2, 1));
plot(x = gen_var[,1], y = destablised, type = "b", lwd = 2, ylim = c(0, 0.02),
     xlab = "Species number", ylab = "Proportion of communities",
     cex.axis = 1.5, cex.lab = 1.5, lty = "dashed");
polygon(x = c(gen_var[,1], rev(gen_var[,1]), -1), 
        y = c(stable + destablised, rep(-1, 8)), 
        col = "grey", border = NA);
box();
points(x = gen_var[,1], y = destablised, type = "b", lwd = 2, lty = "dashed");
points(x = gen_var[,1], y = stabilised, type = "b", lwd = 2, ylim = c(0, 0.02),
       lty = "solid", pch = 20);
legend(x = 5.25, y = 0.02, lwd = 2, cex = 1.25,
       legend = c("Stabilised", "Destabilised"),
       lty = c("solid", "dashed"));
```

>>>>

```{r, echo = TRUE, eval = TRUE}
gen_var     <- read.table(file = "full_data.csv", header = TRUE, sep = ",");
tot_sim     <- sum(gen_var[1,2:5]);
unstable    <- gen_var[,2] / tot_sim;
stable      <- gen_var[,3] / tot_sim;
destablised <- gen_var[,4] / tot_sim;
stabilised  <- gen_var[,5] / tot_sim;
par(mar = c(5, 5, 2, 1));
plot(x = gen_var[,1], y = destablised, type = "b", lwd = 2, ylim = c(0, 0.02),
     xlab = "Species number", ylab = "Proportion of communities",
     cex.axis = 1.5, cex.lab = 1.5, lty = "dashed");
polygon(x = c(gen_var[,1], rev(gen_var[,1]), -4), 
        y = c(stable + destablised, rep(-1, 20)), 
        col = "grey", border = NA);
box();
points(x = gen_var[,1], y = destablised, type = "b", lwd = 2, lty = "dashed");
points(x = gen_var[,1], y = stabilised, type = "b", lwd = 2, ylim = c(0, 0.02),
       lty = "solid", pch = 20);
legend(x = 12, y = 0.02, lwd = 2, cex = 1.5,
       legend = c("Stabilised", "Destabilised"),
       lty = c("solid", "dashed"));
```
